Highly Available Transactions: Virtues and Limitations

### 2013-04-25 writeup/evaluation.tex

\vspace{.5em}\noindent\textbf{Serializability} To establish a serial
order on transactions, algorithms for achieving serializability of
general-purpose read-write transactions in a distributed
setting~\cite{bernstein-book} can require at least one round trip time
(RTT) before committing. As an example, traditional two-phase locking
for a transaction of length $T$ can require $T$ \texttt{lock}
operations and will require at least one \texttt{lock} and
\texttt{unlock} operation.  In a distributed environment, each of
these operations requires coordination, either with other database
servers or with a lock service. If this coordination mechanism is
unavailable, transactions cannot safely commit. Similarly, optimistic
concurrency control requires coordinating via a validation step, while
deterministic transaction scheduling~\cite{deterministic-scheduling}
requires a scheduler. Serializability under multi-version concurrency
control also requires checking for update conflicts. The reliance on a
globally agreed total order necessitates a minimum of one round-trip
to a designated master or coordination service for each of these
classic algorithms.  The cost of round trips will be determined by the
deployment environment, as we saw in Section~\ref{sec:motivation}; we
will demonstrate this cost on public cloud infrastructure in the next
section.

\vspace{.5em}\noindent\textbf{Non-serializability} Many existing
distributed implementations of weak isolation are not highly
available. Lock-based proposals such as those used to provide weak
isolation in Gray's original proposal~\cite{gray-isolation} do not
degrade gracefully in the presence of partial failures. (Note,
however, that lock-based protocols \textit{do} offer the benefit of
recency guarantees.) While multi-versioned storage systems allow for a
variety of transactional guarantees, we have not seen proposals for
truly weak isolation (e.g., non-``tentative update'' schemes) in this
context.  The MDCC~\cite{mdcc} protocol offers Read Committed
isolation with Lost Update avoidance but is similarly unavailable due
to its reliance on preventing write conflicts. Chan and Gray's
read-only transactions provide read-only transactions with item-cut
isolation, causal consistency, and transactional atomicity (session
PL-2L~\cite{adya}) but are unavailable in the presence of coordinator
failure~\cite{readonly}, similar to read-only and write-only
transactions more recently proposed by Eiger~\cite{eiger}; Causal
Serializability offers a similar model (with unavailable
implementation): causal consistency with a variant of Read Uncommitted
between transactions that write to the same data
item~\cite{raynal-causal}.  Brantner's S3 database~\cite{kraska-s3}
and Bayou~\cite{sessionguarantees} can all provide variants of session
PL-2L with high availability, but none provide this HAT functionality
without substantial modification; Swift~\cite{swift} and bolt-on
causal consistency~\cite{bolton} are closest to providing full HAT
semantics operation in a sticky context. As seen, it is possible to
implement many guarantees weaker than serializability---including
guarantees that are achievable with high availability---and still not
achieve high availability.

@@

Thus far, we have largely ignored the question of which applications
require semantics that are unavailable to HATs. As we showed in
Section~\ref{sec:hats}, the main cost of choosing HATs comes in the
inability to prevent Lost Update, Write Skew, and provide recency
bounds. In this section, we attempt to understand when these
guarantees matter both abstractly and in a representative
transactional application based on the TPC-C benchmark~\cite{tpcc}.

\vspace{.5em}\noindent\textbf{Commutativity and Monotonicity} Recent
work on the CALM Theorem~\cite{calm} and Commutative and Replicated
Data Types~\cite{crdt} demonstrates that, if updates logically
commute, then they can often be safely performed in different orders
at different replicas. Accordingly, as long as all writes are
delivered to all replicas, then a system executing monotonic logic
with commutative operators may not suffer from application-level
consistency anomalies as a result of Lost Update or Write Skew
anomalies. However, applications with non-monotonic state mutation
will not, in general, be able to maintain application-level
consistency constraints with HATs alone--in particular, applications
requiring bounded update visibility latency should opt for
unavailability.

\vspace{.5em}\noindent\textbf{TPC-C} To better understand the impact
of HAT-compliance in an application context, we consider a concrete
application: the TPC-C benchmark~\cite{tpcc}. Surprisingly, four of
five transactions can be executed with HATs, while the fifth may
require unavailability.

TPC-C consists of five transactions, capturing the operation of a
wholesale warehouse, including sales, payments, and deliveries. Two
transactions---\textit{Order-Status} and \textit{Stock-Level}---are
read-only and can be executed safely under HATs. Clients may read
stale data, but this does not violate TPC-C requirements and clients
will read their writes if they are sticky-available. Another
transaction type, \textit{Payment}, updates running balances for
warehouses, districts, and customer records as well as providing an
audit trail. The transaction is increment- and append-only, so all
balance increase operations commute, and TA allows the
maintenance of any foreign-key constraints (e.g.,
\texttt{UPDATE/DELETE CASCADE}).

@@

New-Order presents two challenges: ID assignment and stock
maintenance. First, each New-Order transaction requires a unique ID
number for the order. We can create a unique number by, say,
concatenating the client ID and a timestamp. However, the TPC-C
specification requires order numbers to be \textit{sequentially}
assigned within a district, which requires preventing Lost
Update. Accordingly, HATs cannot provide compliant TPC-C execution but
can stil maintain uniqueness constraints. Second, the New-Order transaction
decrements inventory counts: what if the count becomes negative?
Fortunately, TPC-C New-Order restocks each item's inventory count
(increments by 91) if it would become negative as the result of
placing an order. This means that, even in the presence of concurrent
New-Orders, an item's stock will never fall below zero. This is TPC-C
compliant, but a HAT system might end up with more stock
than in a non-HAT-compliant implementation.

Delivery is challenging due to non-monotonicity. Each Delivery deletes
a pending order from the New-Order table and should be idempotent in
order to avoid billing a customer twice; this implies a need to
prevent Lost Update. This issue  can be avoided  by moving the
non-monotonicity to the real world---the carrier that picks up the
package for an order can ensure that she is the only carrier who has
done so---but cannot provide a correct execution with HATs
alone. However, according to distributed transaction
architects~\cite{entitygroup}, these compensatory actions are
relatively common in real-world business processes.

@@

In summary, many---but not all---TPC-C transactions are well-served by
HATs. The two problematic transactions---New-Order and Payment---rely
on non-monotonic state update. The former transaction can be modified
to ensure ID uniqueness at the expense of sequential per-district ID
ordering, while the latter is an inherently non-monotonic action
requiring external compensation or stronger consistency protocols. We
expect that, especially for read-dominated workloads found in many
online services, HAT guarantees will suffice for many application
transactions.

\subsection{Experimental Costs}

>>>>

\vspace{.5em}\noindent\textbf{Serializability} To establish a serial
order on transactions, algorithms for achieving serializability of
general-purpose read-write transactions in a distributed
setting~\cite{bernstein-book} requires at least one round trip time
(RTT) before committing. As an example, traditional two-phase locking
for a transaction of length $T$ may require $T$ \texttt{lock}
operations and will require at least one \texttt{lock} and
\texttt{unlock} operation.  In a distributed environment, each of
these operations requires coordination, either with other database
servers or with a lock service. If this coordination mechanism is
unavailable, transactions cannot safely commit. Similarly, optimistic
concurrency control requires coordinating via a validation step, while
deterministic transaction scheduling~\cite{deterministic-scheduling}
requires a scheduler. Serializability under multi-version concurrency
control requires checking for update conflicts. All told, the reliance
on a globally agreed total order necessitates a minimum of one
round-trip to a designated master or coordination service for each of
these classic algorithms.  The cost of round trips will be determined
by the deployment environment, as we saw in
Section~\ref{sec:motivation}; we will demonstrate this cost on public
cloud infrastructure in Section~\ref{sec:prototype}.

\vspace{.5em}\noindent\textbf{Non-serializability} Most existing
distributed implementations of weak isolation are not highly
available. Lock-based proposals such as those used to provide weak
isolation in Gray's original proposal~\cite{gray-isolation} do not
degrade gracefully in the presence of partial failures. (Note,
however, that lock-based protocols \textit{do} offer the benefit of
recency guarantees.) While multi-versioned storage systems allow for a
variety of transactional guarantees, few offer traditional weak
isolation (e.g., non-``tentative update'' schemes) in this context.
The MDCC~\cite{mdcc} protocol offers Read Committed isolation with
Lost Update avoidance but is similarly unavailable due to its reliance
on preventing write conflicts. Chan and Gray's read-only transactions
provide read-only transactions with item-cut isolation, causal
consistency, and transactional atomicity (session PL-2L~\cite{adya})
but are unavailable in the presence of coordinator
failure~\cite{readonly}, similar to read-only and write-only
transactions more recently proposed by Eiger~\cite{eiger}. Causal
Serializability offers a similar model (with unavailable
implementation): causal consistency with a variant of Read Uncommitted
between transactions that write to the same data
item~\cite{raynal-causal}.  Brantner's S3 database~\cite{kraska-s3}
and Bayou~\cite{sessionguarantees} can all provide variants of session
PL-2L with high availability, but none provide this HAT functionality
without substantial modification. Swift~\cite{swift} and bolt-on
causal consistency~\cite{bolton} are closest to providing maximum
sticky HAT semantics. As we have seen, it is possible to implement many
guarantees weaker than serializability---including guarantees that are
achievable with high availability---and still not achieve high
availability.

@@

Thus far, we have largely ignored the question of when HAT semantics
are useful (or otherwise are too weak). As we showed in
Section~\ref{sec:hats}, the main cost of high availability and low
latency comes in the inability to prevent Lost Update, Write Skew, and
provide recency bounds. In this section, we attempt to understand when
these guarantees matter both abstractly and in a representative
transactional application based on the TPC-C benchmark~\cite{tpcc}.

\vspace{.5em}\noindent\textbf{Commutativity and Monotonicity} Recent
work on the CALM Theorem~\cite{calm} and Commutative and Replicated
Data Types~\cite{crdt} demonstrates that, if updates logically
commute, then they can often be safely performed in different orders
at different replicas. Accordingly, as long as all writes are
delivered to all replicas, then a system executing monotonic logic
with commutative operators may not suffer from application-level
consistency anomalies as a result of Lost Update or Write Skew
anomalies. However, applications with non-monotonic state mutation
will not, in general, be able to maintain application-level
consistency constraints with HATs alone---in particular, applications
requiring bounded update visibility latency should opt for
unavailability.

\vspace{.5em}\noindent\textbf{TPC-C} To better understand the impact
of HAT-compliance in an application context, we consider a concrete
application: the TPC-C benchmark. In brief, we find that four of five
transactions can be executed with HATs, while the fifth may require
unavailability.

TPC-C consists of five transactions, capturing the operation of a
wholesale warehouse, including sales, payments, and deliveries. Two
transactions---\textit{Order-Status} and \textit{Stock-Level}---are
read-only and can be executed safely with HATs. Clients may read stale
data, but this does not violate TPC-C requirements and clients will
read their writes if they are sticky-available. Another transaction
type, \textit{Payment}, updates running balances for warehouses,
districts, and customer records and provides an audit trail. The
transaction is increment- and append-only, so all balance increase
operations commute, and TA allows the maintenance of foreign-key
integrity constraints (e.g., via \texttt{UPDATE/DELETE CASCADE}).

@@

The New-Order transaction presents two challenges: ID assignment and
stock maintenance. First, each New-Order transaction requires a unique
ID number for the order. We can create a unique number by, say,
concatenating the client ID and a timestamp. However, the TPC-C
specification requires order numbers to be \textit{sequentially}
assigned within a district, which requires preventing Lost
Update. Accordingly, HATs cannot provide compliant TPC-C execution but
can stil maintain uniqueness constraints. Second, the New-Order
transaction decrements inventory counts: what if the count becomes
negative?  Fortunately, TPC-C New-Order restocks each item's inventory
count (increments by 91) if it would become negative as the result of
placing an order. This means that, even in the presence of concurrent
New-Orders, an item's stock will never fall below zero. This is TPC-C
compliant, but a HAT system might end up with more stock than in a
non-HAT-compliant implementation.

The Delivery transaction is challenging due to non-monotonicity. Each
Delivery deletes a pending order from the New-Order table and should
be idempotent in order to avoid billing a customer twice; this implies
a need to prevent Lost Update. This issue can be avoided by moving the
non-monotonicity to the real world---the carrier that picks up the
package for an order can ensure that she is the only carrier who has
done so---but cannot provide a correct execution with HATs
alone. However, according to distributed transaction
architects~\cite{entitygroup}, these compensatory actions are
relatively common in real-world business processes.

@@

In summary, many---but not all---TPC-C transactions are well-served by
HATs. The two problematic transactions---New-Order and Payment---rely
on non-monotonic state update. The former can be modified to ensure ID
uniqueness but not sequential ID ordering, while the latter is an
inherently non-monotonic action requiring external compensation or
stronger consistency protocols. Based on these experiences and
discussions with practitioners, we expect that, especially for
read-dominated workloads found in many online services, HAT guarantees
will provide useful semantics for many applications.

\subsection{Experimental Costs}
\label{sec:prototype}

### 2013-04-25 writeup/futurework.tex
fixed
final pageshorten
editing pass

\textbf{What are the limits of achievable HAT models, and how are they
  defined?}  In this work, we have taxonomized several well-defined
and well-documented semantic properties. This is useful as it
contextualizes decades of existing database and distributed systems
design and algorithms but does not provide guidance as to what
consistency models are the ``strongest''---or admit the smallest set
of executions---within each availability class. A recent report from
UT Austin shows that no model stronger than causal consistency can be
achieved in a sticky highly available, one-way convergent
system~\cite{cac}, but there are infinite highly available and sticky
highly available models to consider. For example, always returning the
value $1$ in response to reads is incomparable with (i.e., neither
stronger nor weaker than) causal consistency: returning $1$ does not
respect causality, and causal consistency returns values other than
$1$. Always returning the value $2$ is similarly incomparable, and, as
an example, we can enumerate models that return all integers and real
numbers--an uncountably infinite set of models. Given these infinite
models, are there meaningful properties that delineate the boundaries
between classes of highly available systems? Is there a
``meta-property'' that exactly characterizes what properties are
achievable with high availability or sticky high availability? This is
an area of ongoing research within the Berkeley HAT project.

\textbf{What are the costs and benefits within HAT designs?} There are
many possible combinations of HAT guarantees, and the performance and
ease of implementation of a HAT system will vary depending on which
guarantees it provides. For example, as we have discussed, the cost in
moving from a sticky high available implementation of highly available
guarantees to a truly highly available system seems expensive for some
models (e.g., metadata requirements or visibility requirements may
become problematic). Further experimentation regarding the set of
useful and achievable HAT guarantees will shed further light on this
question.

\textbf{Where do semantics-based concurrency control and weakened
  failure models lie in the HAT landscape?} The vast
literature on semantics-based concurrency control indicates 
when coordination can be avoided while providing ``strongly
consistent'' outcomes for limited failure scenarios. We have performed
a narrow case study, but a general taxonomization of
techniques such as escrow transactions~\cite{escrow},
Sagas~\cite{sagas}, and other long-running transaction support could
help answer the challenge of programming in a weakly consistent
environment. HAT guarantees can also be strengthened by considering
weaker failure models such as bounded asynchrony or models in which
the underlying hardware provides explicit service-level
agreements. Additionally, while we have focused on systems that
provide a single availability mode, there are several interesting
hybrids to consider. For example, a system may provide ``best-effort''
stickiness (or serializability) in the absence of partitions, but, in
the presence of partitions, ``lose'' guarantees by having clients
reconnect to an available replica. This strategy provides stronger
guarantees in the absence of partitions but, to provide availability,
sacrifices them in the event of partitions.

>>>>

\textbf{What are the limits of HAT semantics?}  In this work, we have
taxonomized several well-defined and well-documented semantic
properties. This is useful as it contextualizes existing database and
distributed systems semantics but does not provide guidance as to what
consistency models are the ``strongest''---or admit the smallest set
of executions---within each availability class. A recent report from
UT Austin shows that no model stronger than causal consistency can be
achieved in a sticky highly available, one-way convergent
system~\cite{cac}, but there are infinite highly available and sticky
highly available models to consider. For example, always returning the
value $1$ in response to reads is incomparable with (i.e., neither
stronger nor weaker than) causal consistency: returning $1$ does not
respect causality, and causal consistency returns values other than
$1$. There are actually infintely many incomparable models (vacuously:
return $1$, return $2$, and so on). Are there \textit{meaningful}
properties that delineate the boundaries between availability levels?
Is there a ``meta-property'' that exactly characterizes what
properties are achievable with high availability or sticky high
availability? This is an area of ongoing research within the Berkeley
HAT project. \pbnote{SHORTEN}

\textbf{What are the costs and benefits within HAT designs?} There are
many possible combinations of HAT guarantees, and the performance and
ease of implementation of a HAT system will vary depending on which
guarantees it provides. For example, as we have discussed, the cost in
moving from a sticky high available implementation of highly available
guarantees to a truly highly available system seems expensive for some
models (e.g., metadata requirements or visibility penalties may
become problematic). Further experimentation regarding the set of
useful and achievable HAT guarantees will shed further light on this
question.

\textbf{Where do semantics-based concurrency control and weakened
  failure models lie in the HAT landscape?} The vast literature on
semantics-based concurrency control indicates when coordination can be
avoided while providing ``consistent'' operation for limited failure
scenarios. We have performed a narrow case study, but a general
taxonomization of techniques such as escrow
transactions~\cite{escrow}, Sagas~\cite{sagas}, and other long-running
transaction support could help address the challenge of programming in
a weakly consistent environment. HAT guarantees can also be
strengthened by considering weaker failure models such as networks
with bounded asynchrony. Additionally, while we have focused on
systems that provide a single availability mode, there are several
interesting hybrids to consider. For example, a system may provide
strong semantics in the absence of partitions, but, in the presence of
partitions, ``lose'' guarantees by having clients reconnect to an
available replica. This provides ``best effort'' guarantees but, to
provide availability, sacrifices them in the event of partitions.

### 2013-04-25 writeup/hat-appendix.tex

@@

@@

>>>>

\begin{figure}[H]
\begin{align*}
\small
T_1 &: w_x(1)\\
T_2 &: w_y(1)\\
T_3 &: r_y(1)~r_x(0)
\end{align*}
\caption{Example of \textit{N-MW} anomaly if $T_2$ directly session-depends on $T_1$.}
\label{fig:nmw-history}
\end{figure}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=3cm]
\tikzstyle{tx}=[draw=none, fill=none]
\node[tx] (T1) at (0,0) {$T_1$};
\node[tx] (T2) at (2,0) {$T_2$};
\node[tx] (T3) at (2,-1) {$T_3$};

\draw[->] (T1) edge node[above]{$s_i$} (T2);
\draw[->] (T2) edge node[right]{$wr_y$} (T3);
\draw[->, dashed] (T3) edge node[below, sloped]{$rw_x$} (T1);
\end{tikzpicture}
\caption{DSG for Figure~\ref{fig:nmw-history}.}
\label{fig:nmw-dsg}
\end{figure}

@@

\begin{figure}[H]
\begin{align*}
\small
T_1 &: w_x(1)\\
T_2 &: r_x(1) w_y(1)\\
T_3 &: r_y(1)~r_x(0)
\end{align*}
\caption{Example of \textit{N-WFR} anomaly.}
\label{fig:nwfr-history}
\end{figure}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=3cm]
\tikzstyle{tx}=[draw=none, fill=none]
\node[tx] (T1) at (0,0) {$T_1$};
\node[tx] (T2) at (2,0) {$T_2$};
\node[tx] (T3) at (2,-1) {$T_3$};

\draw[->] (T1) edge node[above]{$wr_x$} (T2);
\draw[->] (T2) edge node[right]{$wr_y$} (T3);
\draw[->, dashed] (T3) edge node[below, sloped]{$rw_x$} (T1);
\end{tikzpicture}
\caption{DSG for Figure~\ref{fig:nwfr-history}.}
\label{fig:nwfr-dsg}
\end{figure}

@@

\begin{figure}[H]
\begin{align*}
\small
T_1 &: w_x(1)\\
T_2 &: r_x(0)\\
\end{align*}
\caption{Example of \textit{N-RYW} anomaly if $T_2$ directly session-depends on $T_1$.}
\label{fig:nryw-history}
\end{figure}

\draw[->] (T1) edge node[above]{$s_i$} (T2);
\draw[dashed, ->] (T2) edge [bend left] node[below]{$rw_x$} (T1);
\end{tikzpicture}
\caption{DSG for Figure~\ref{fig:nwfr-history}.}
\label{fig:nryw-dsg}
\end{figure}

### 2013-04-25 writeup/model.tex
another pass

To understand which guarantees can be provided with high availabilty,
we must first define what high availability means. In this section, we
will formulate a model that captures a range of availability models,
including ``true'' high availability, availability with stickiness,
and several other useful variants.

Informally, highly available algorithms ensure ``always on'' operation
and guaranteed low latency. If users of a highly available system are
able to contact a (set of) server(s) in a system, they are guaranteed
a response; this means servers will not need to communicate with any
others. If servers are partitioned from one another, they do not need
to stall in order to provide a ``safe'' query response. This lack of
fast-path coordination also means that a highly available system also
provides low latency~\cite{abadi-pacelc}; in a wide-area setting, this
means that clients need not wait for cross-datacenter
communication. To properly describe whether a \textit{transactional}
system is highly available, we need to describe what servers a client
must contact as well as what kinds of responses a server can provide,
especially given the possibility of aborts.

@@

Traditionally, a system provides {\em availability} if every user that
can contact a correct server eventually receives a response from that
server, even in the presence of arbitrary, indefinitely long network
partitions between servers~\cite{gilbert-cap}.\footnote{Under this
  definition, a system that requires a majority of servers to be
  online is not available.} As in a standard distributed database,
designated servers might handle operations on different data
items;\footnote{There is a further distinction between a \textit{fully
    replicated} system, in which all servers are replicas for all data
  items, and a \textit{partially replicated} system, in which at least
  one server acts as a replica for only a subset of all data
  items. For generality, and, for applicability to many modern
  ``sharded'' or ``partitioned'' data storage systems~\cite{dynamo,
    pnuts, bigtable, spanner, hstore}, we consider partially
  replicated systems.} a server that can handle an operation for a
given data item is called a \textit{replica} for that item. While this
standard model is useful, there are several other cases we should
consider.

@@

We have so far focused on single-object, single-operation
availability. This is standard in the distributed systems literature
(e.g., distributed register models such as linearizability all
concern single objects~\cite{herlihy-art}), yet the database
literature largely focuses on transactions: groups of multiple
operations over multiple objects. Accordingly, by itself, replica
availability is insufficient to describe availability guarantees for
transactions. Additionally, given the choice of \textit{commit} and
\textit{abort} responses---which signal transaction success or failure
to a client---we must take care in defining transactional availability.

>>>>

To understand which guarantees can be provided with high availabilty,
we must first define what high availability means. In this section, we
will formulate a model that captures a range of availability models,
including ``true'' high availability, availability with stickiness,
and transactional availability.

Informally, highly available algorithms ensure ``always on'' operation
and guaranteed low latency. If users of a highly available system are
able to contact a (set of) server(s) in a system, they are guaranteed
a response; this means servers will not need to communicate with any
others. If servers are partitioned from one another, they do not need
to stall in order to provide clients a ``safe'' response to
operations. This lack of fast-path coordination also means that a
highly available system also provides low latency~\cite{abadi-pacelc};
in a wide-area setting, this means that clients need not wait for
cross-datacenter communication. To properly describe whether a
\textit{transactional} system is highly available, we need to describe
what servers a client must contact as well as what kinds of responses
a server can provide, especially given the possibility of aborts.

@@

Traditionally, a system provides {\em availability} if every user that
can contact a correct server eventually receives a response from that
server, even in the presence of arbitrary, indefinitely long network
partitions between servers~\cite{gilbert-cap}.\footnote{Under this
  definition, a system that requires a majority of servers to be
  online is not available.} As in a standard distributed database,
designated servers might perform operations for different data items;
a server that can handle an operation for a given data item is called
a \textit{replica} for that item.\footnote{There is a further
  distinction between a \textit{fully replicated} system, in which all
  servers are replicas for all data items, and a \textit{partially
    replicated} system, in which at least one server acts as a replica
  for only a subset of all data items. For generality, and, for
  applicability to many modern ``sharded'' or ``partitioned'' data
  storage systems~\cite{dynamo, pnuts, bigtable, spanner, hstore}, we
  consider partially replicated systems.} While this standard model is
useful, there are several other cases we should consider.

@@

Until now, we have considered single-object, single-operation
availability. This is standard in the distributed systems literature
(e.g., distributed register models such as linearizability all concern
single objects~\cite{herlihy-art}), yet the database literature
largely focuses on transactions: groups of multiple operations over
multiple objects. Accordingly, by itself, replica availability is
insufficient to describe availability guarantees for
transactions. Additionally, given the choice of \textit{commit} and
\textit{abort} responses---which signal transaction success or failure
to a client---we must take care in defining transactional
availability.
